Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-30 main-disk-model.tex
text about fork instance, example not quite accurate yet

%    \subsection{The fork}
%    We look at the behavior of these heuristics on a fork graph,
%    where there is a root task~$T_0$, producing $n$ files $f_1, \ldots, f_n$
%    to be used by tasks $T_1, \ldots, T_n$ ($f_i = c_{0,i}$).
%
%    Without memory, this problem is NP-complete; this is equivalent
%    to 2-partition if the tasks have $w_i=a_i$, and all files are of size~$f_i=0$,
%    and with two processors. Half of the tasks must be sent to the processor
%    on which $T_0$ is not executed, and the optimal makespan is
%    $w_0+\frac{1}{2}\sum_{1\leq i \leq n} w_i$.
%
%    However, with an infinite number of identical processors, it can be
%    solved in polynomial time: sort tasks by non-decreasing $f_i+w_i$;
%    the $k$ tasks with smallest $f_i+w_i$ are then sent to another processor,
%    while the remaining $n-k$ tasks are executed locally (try all values of $k$).
%
%    With heterogeneous processors, it is probably NP-complete again
%    because we could ensure that there are only two processors fast enough
%    and get back to the 2-partition...
%
%    We also had an example where evicting large files first in step 2
%    can lead to arbitrarily bad makespan. Consider a fork with $n=2$,
%    $f_1=1$, $w_1=2$, $f_2=100$, $w_2=1$, and memory constraint
%    imposes that we free one unit of memory before executing one
%    of the tasks\ldots Actually the new version with BLC would start
%    considering $T_2$ and be fine in this case\ldots
%
%
%    \AB{Can we prove that we have (maybe) a 2-approximation,
%        at least for the fork? What worst-case can we think of? }

>>>>

\hmey{BEGIN FORK}
    \subsection{The fork}
    We look at the behavior of these heuristics on a fork graph,
    where there is a root task~$T_0$, producing $n$ files $f_1, \ldots, f_n$
    to be used by tasks $T_1, \ldots, T_n$ ($f_i = c_{0,i}$).

    Without memory, this problem is NP-complete; this is equivalent
    to 2-partition if the tasks have $w_i=a_i$, and all files are of size~$f_i=0$,
    and with two processors. Half of the tasks must be sent to the processor
    on which $T_0$ is not executed, and the optimal makespan is
    $w_0+\frac{1}{2}\sum_{1\leq i \leq n} w_i$.

    However, with an infinite number of identical processors, it can be
    solved in polynomial time: sort tasks by non-decreasing $f_i+w_i$;
    the $k$ tasks with smallest $f_i+w_i$ are then sent to another processor,
    while the remaining $n-k$ tasks are executed locally (try all values of $k$).

    With heterogeneous processors, it is probably NP-complete again
    because we could ensure that there are only two processors fast enough
    and get back to the 2-partition...

    We also had an example where evicting large files first in step 2
    can lead to arbitrarily bad makespan. Consider a fork with $n=2$,
    $f_1=1$, $w_1=2$, $f_2=100$, $w_2=1$, and memory constraint
    imposes that we free one unit of memory before executing one
    of the tasks\ldots Actually the new version with BLC would start
    considering $T_2$ and be fine in this case\ldots

\begin{figure}[tb]
  \centering
  \includegraphics[width=0.5\columnwidth]{images/bad-blc-instance.png} \\[1ex]
  \includegraphics[width=0.999\columnwidth]{images/blc-bad-cost.png} \\[1ex]
  \includegraphics[width=0.58\columnwidth]{images/opt-cost.png}
  \caption{Top: Example instance $I$, middle: BLC applied to $I$ leads to makespan $w_0 + nk/2 + k$, bottom: optimal solution has makespan $w_0 + n/2$.
  \hmey{TODO: adapt resolution of figure and fix $\epsilon$ problem}}
  \label{fig:fork-bad-blc-instance}
\end{figure}

Figure~\ref{fig:fork-bad-blc-instance} shows an instance where \heftblc\ performs very poorly.
Since the sorting criterion $w_i + c_{0i}$ yields an arbitrary ordering of the tasks $T_i$ (with $1 \leq i \leq n$), we may
assume that the algorithm processes the nodes in level $1$ of instance $I$ from left to right. 
As shown in the middle part of the figure, $T_1$ is processed...
\hmey{TODO: adapt with $\epsilon$ to enforce even tasks to be ``sent away''}
This leads to a makespan
of $w_0 + nk/2 + k$. The optimal solution, in turn, as shown in the bottom,
requires only $w_0 + n/2$ timesteps. Since $k$ can be chosen arbitrarily large if the value $10$ is scaled accordingly,
this instance shows that \heftblc\ may yield solutions with an arbitrarily large gap to optimality.

\AB{Can we prove that we have (maybe) a 2-approximation,
        at least for the fork? What worst-case can we think of? }
\hmey{END FORK}
